Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-05-06 ms.tex
I made the tex file one sentence per line to make it work better with version control.
I added aastex6.cls as an optional manuscript style.
I explained the colors in the saturation limits plot.

%\documentclass{article}
%\documentclass[manuscript]{aastex}
\documentclass[iop]{emulateapj}

@@

\begin{table}
%\centering
\begin{tabular}{ccr}
		& DHS	& Grism \\
 \hline \hline		
Resolution &  \DHSres & 1770 \\
Dispersion & 0.29 nm / px & 1.0 nm / px \\
Wavelengths & 1.01 - 2.02$\mu$m (F150W2)\footnote{There is a 0.05$\mu$m gap between detectors that depends on field position} & 2.44 - 4.02$\mu$m (F322W2)\\
				& 								& 3.88 - 4.98$\mu$m (F444W) \\
Plate Scale & 32 mas/px  &  65 mas / px\\
\hline
\end{tabular}
\caption{Properties of DHS and simultaneous long-wavelength grism spectra.}\label{tab:DHSgprop}
\vspace{0.1in}
\end{table}

@@

%The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs. The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m. If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right). These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard. Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ C grism estimate}.}\label{fig:DHSimage}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{dhs_pupil_overlay.png}
\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}.  . The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (black lines). The circles in the image are products of the OSIM (optical telescope element simulator) test source used in Cryogenic Vacuum testing of the instrument suite, and will not be present in flight. The pupil wheel is clocked to make the DHS spectra straight along rows, but moves the DHS elements off-center from JWST's pupil and masks. \textbf{Remove circles and secondary struts from Orange}}\label{fig:DHSvsPupilOverlay}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{readout_schematic.pdf}
\caption{Schematic of example readout modes for an exposure that is 12 frame times in duration. A single FITS file is saved for the exposure, consisting of 1-2 groups (read 1 or both read 1 and read 2) per integration. No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable. The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but will saturate more easily. }\label{fig:readout}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star. The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.}\label{fig:DHSaps}
\end{figure}

@@

%The DHS improves constraints on HD209458b's temperature (assumed isothermal in this model), abundances and cloud pressure layer, as visible in Figure \ref{fig:cornerRun}. The improvements in abundances are

>>>>

%\documentclass{article}
%\documentclass[twocolumn]{aastex6}
\documentclass[iop]{emulateapj}

@@

\begin{table}
\centering
\begin{tabular}{ccr}
		& DHS	& Grism \\
 \hline \hline		
Resolution &  \DHSres & 1770 \\
Dispersion & 0.29 nm / px & 1.0 nm / px \\
Wavelengths & 1.01 - 2.02$\mu$m (F150W2)\footnote{There is a 0.05$\mu$m gap between detectors that depends on field position} & 2.44 - 4.02$\mu$m (F322W2)\\
				& 								& 3.88 - 4.98$\mu$m (F444W) \\
Plate Scale & 32 mas/px  &  65 mas / px\\
\hline
\end{tabular}
\caption{Properties of DHS and simultaneous long-wavelength grism spectra.}\label{tab:DHSgprop}
\vspace{0.1in}
\end{table}

@@

%The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs.
%The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m.
%If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
\caption{Example images of the same source observed simultaneously with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right).
These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard.
Only 3 detectors will be needed for transit observations \textbf{Update w/ Mod A image and w/ C grism estimate}.}\label{fig:DHSimage}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{dhs_pupil_overlay.png}
\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}. 
The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (black lines).
The circles in the image are products of the OSIM (optical telescope element simulator) test source used in Cryogenic Vacuum testing of the instrument suite, and will not be present in flight.
The pupil wheel is clocked to make the DHS spectra straight along rows, but moves the DHS elements off-center from JWST's pupil and masks.
\textbf{Remove circles and secondary struts from Orange}}\label{fig:DHSvsPupilOverlay}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{readout_schematic.pdf}
\caption{Schematic of example readout modes for an exposure that is 12 frame times in duration.
A single FITS file is saved for the exposure, consisting of 1-2 groups (read 1 or both read 1 and read 2) per integration.
No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but will saturate more easily.}\label{fig:readout}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:DHSaps}
\end{figure}

@@
